A comparison of classification algorithms applied to the Adult Database

### 2009-12-10 report/final.tex
finishing CN2 experimental results description.

\begin{table}
\begin{center}
\begin{tabular}{ | l | l | l | l | l |}
    \hline
    \textbf{Algorithm} & \textbf{Error estimate} & \textbf{Train error rate} & \textbf{Test error rate} & \textbf{Time} \\ \hline
    Unordered & Laplacian & 13.3 & 15.2 & 3min29sec \\ \hline
    Unordered & Naive & - & - & - \\ \hline
    Ordered & Laplacian & 0 & 17.6 & 1min45sec \\ \hline
    Ordered & Naive & 0 & 19.9 & 12min21sec \\ \hline
\end{tabular}
\caption{Results for CN2.}
\label{tbl:results_cn2}
\end{center}
\end{table}

@@

>>>>

\begin{table}
\begin{center}
\begin{tabular}{ | l | l | l | l | l |}
    \hline
    \textbf{Algorithm} & \textbf{Error estimate} & \textbf{Train error rate} & \textbf{Test error rate} & \textbf{Time} \\ \hline
    Unordered & Laplacian & 13.3 & 15.2 & 3min29sec \\ \hline
    Unordered & Naive & - & - & - \\ \hline
    Ordered & Laplacian & 0 & 17.6 & 1min45sec \\ \hline
    Ordered & Naive & 0 & 19.9 & 12min21sec \\ \hline
    Ordered & Information Gain & 18.9 & 18.9 & 5sec \\ \hline
    Ordered & Modified Entropy & 18.9 & 19.1 & 20sec \\ \hline
\end{tabular}
\caption{Results for CN2.}
\label{tbl:results_cn2}
\end{center}
\end{table}

The information gain and modified entropy approaches to error estimations are
only available for the algorithm producing ordered set of rules. The approach
building an unordered set of rules with a naive error estimation lead to a stack
overflow error in the application. One thing one can note is that the process of
building classification rules takes, in average, longer than the one of building
classification trees. Nevertheless, the results are arguably more expressive and
the error rates are low (the best being 15.2\% for a previously unkown set of 
examples). Also note that the variant of building an ordered set of rules with
an information gain error estimate produces rules faster and with an acceptable
error rate (18.9\%). To analyze the expressiveness of the rules produced, a set
of rules that cover the most examples of the training data are described in 
listing \ref{cn2_rules} (using the ordered algorithm with the laplacian error 
estimation).

@@

\clearpage
\section{Classification Rules}
\begin{lstlisting}[language=c,frame=single,breaklines=true,basicstyle=\footnotesize\ttfamily,caption={Subset of the ordered set of rules induced by CN2 with the laplacian error estimation method},label=cn2_rules]
IF    age < 20.50
  AND capital_gain < 9720.00
  AND hours_per_week < 59.00
THEN  class = less_or_equal_than_50K  [0 2366]
ELSE
IF    19.50 < age < 21.50
  AND marital_status = never_married
  AND capital_gain < 67047.00
THEN  class = less_or_equal_than_50K  [0 664]
ELSE
IF    age < 54.50
  AND capital_gain > 10585.50
  AND hours_per_week > 33.00
THEN  class = more_than_50K  [520 0]
ELSE
IF    age < 23.50
  AND hours_per_week < 31.00
THEN  class = less_or_equal_than_50K  [0 492]
ELSE
IF    age < 24.50
  AND workclass = private
  AND relationship = own_child
  AND capital_loss < 2129.50
  AND hours_per_week > 32.50
  AND native_country = united_states
THEN  class = less_or_equal_than_50K  [0 562]
ELSE
IF    age < 60.50
  AND 7565.50 < capital_gain < 30961.50
THEN  class = more_than_50K  [445 0]
ELSE
IF    relationship = own_child
  AND race = black
  AND hours_per_week < 49.00
THEN  class = less_or_equal_than_50K  [0 261]
ELSE
IF    age < 38.50
  AND education = hs_grad
  AND marital_status = never_married
  AND relationship = own_child
  AND hours_per_week < 75.00
THEN  class = less_or_equal_than_50K  [0 378]
ELSE
IF    20.50 < age < 23.50
  AND workclass = private
  AND marital_status = never_married
  AND capital_loss < 2116.00
  AND hours_per_week > 32.50
THEN  class = less_or_equal_than_50K  [0 434]
\end{lstlisting}
